\EngAndPor{
  Legal Notes:
  
  There is no warranty for any part of the documented software. The authors have
  taken care in the preparation of this thesis, but make no expressed or implied
  warranty of any kind and assume no responsibility for errors or omissions. No
  liability is assumed for incidental or consequential damages in connection
  with or arising out of the use of the information or programs contained here.
}{
  Notas legais:
  
  Não há garantia para qualquer parte do software documentado. Os autores
  tomaram cuidado na preparação desta tese, mas não fazem nenhuma garantia
  expressa ou implícita de qualquer tipo e não assumem qualquer responsabilidade
  por erros ou omissões. Não se assume qualquer responsabilidade por danos
  incidentais ou consequentes em conexão ou decorrentes do uso das informações
  ou programas aqui contidos.
}

% http://portalbu.ufsc.br/ficha
% http://portal.bu.ufsc.br/servicos/ficha-de-identificacao-da-obra/
\begin{abntexEnvFichacatalografica}
  \vspace*{\fill}

  \begin{center}

    \EngAndPor{%
      Cataloging at source by the
      University Library of the Federal University of Santa Catarina.
    }{%
      Catalogação na fonte pela Biblioteca Universitária da Universidade
      Federal de Santa Catarina.
    }

    \EngAndPor{%
      File compiled at \currenttime{} h of the day \today.
    }{%
      Arquivo compilado às \currenttime{} h do dia \today.
    }

    \framebox[\textwidth]{
      % q/use-the-value-of-title-with-removed-linebreak
      \begin{minipage}{0.98\textwidth}
      \begingroup \let\\=\space

        \ttfamily
        \theauthor{}

        \hspace{0.5cm} \thetitle%
        \UFSCifNotEmpty{\imprimirsubtitulo}{%
          ~:~\imprimirsubtitulo% chktex 39
        }%
        ~/~\theauthor% chktex 39
        {;}~\abnteximprimirorientadorRotulo,~\abnteximprimirorientador%
        \UFSCifNotEmpty{%
          \abnteximprimircoorientador%
        }{%
          {;}~\abnteximprimircoorientadorRotulo,~\abnteximprimircoorientador%
        }%
        ~--~\abnteximprimirlocal,~\ABNTEXimprimirdata.%chktex 39

        % Prints how much pages there are on the document
        % and links to the last page
        \hspace{0.5cm}~\pageref{LastPage} p.
        \bigskip

        \hspace{0.5cm}
        \abnteximprimirtipotrabalho~--~\abnteximprimirinstituicao,
        \imprimircentro,~\imprimirprograma.
        \bigskip

        \hspace{0.5cm} \EngAndPor{Includes references}{Inclui referências}
        \bigskip

        % q/using-lower-case-roman-numerals-in-enumerate-lists
        % q/how-to-define-inparaenum-in-the-preamble
        \hspace{0.5cm}
        \begin{inparaenum}
          \EngAndPor{%
            \palavrasChaveInglescomvirgula%
          }{%
            \palavrasChavePortuguescomvirgula%
          }
        \end{inparaenum}%
        \begin{inparaenum}[I.]
          \item \abnteximprimirorientador{}
          \UFSCifNotEmpty{%
            \abnteximprimircoorientador%
          }{%
            \item \abnteximprimircoorientador~%
          }
          \item \imprimirprograma{}
          \item \thetitle{}
        \end{inparaenum}%
        \bigskip

        \hspace{7.75cm} CDU 02:141:005.7

      \endgroup
      \end{minipage}
    }

  \end{center}

\end{abntexEnvFichacatalografica}
